The Practical Application of Computerised Multistage Tests

### 2021-03-01 article.Rmd
Short summary section

7. Summary

8. References

>>>>

# Summary

We've seen how to take a test from the design stage to validation of the items, Rasch analysis, banking of difficulties, functions for calculation of ability estimates and scale scores, and finally calculation of the cut scores that will be used for routing.

Once this information has been calculated and provided to the test administrators so that they can build it in to the test delivery system the test is theoretically ready for delivery. It is usual at this stage to run a further pilot to iron out any operational issues.

# References
